---
title: "document_process"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)

january_delays <- read_excel(here::here("static", "data", "usethis-reports", "Subway_&_SRT_Logs_January_2019.xlsx"))

january_delays
```
First, I clean the column names.
```{r}
library(dplyr)
library(janitor)

january_delays <- january_delays %>%
  clean_names()
```

Then I want to check that line is one of YU, BD, SHP, SRT

```{r}
library(assertr)

january_delays %>%
  assert(in_set("YU", "BD", "SHP", "SRT"), line)
```
Ok, nope! So I’ll clean up cases where that’s not true.

```{r}
january_delays %>%
  filter(!(line %in% c("YU", "BD", "SHP", "SRT"))) %>%
  count(line)
```

And recode where possible.

```{r}
january_delays <- january_delays %>%
  mutate(line = case_when(line %in% c("B/D", "BD LINE") ~ "BD",
                          line == "YUS" ~ "YU",
                          TRUE ~ line))
```

Then finally exclude cases where it’s still not true.

```{r}
january_delays <- january_delays %>%
  filter(line %in% c("YU", "BD", "SHP", "SRT"))
```

Now the data looks good! But, we only have the code of the delay. There is another data set with the actual description.

```{r}
delay_codes <- read_excel(here::here("static", "data", "usethis-reports", "Subway & SRT Log Codes.xlsx")) %>%
  clean_names()
```

```{r}
visdat::vis_dat(delay_codes)
```

```{r}
delay_codes
```


Because, for some reason, the main subway codes are separate from the SRT codes. It’s ok, I can put them together.


```{r}
delay_codes2 <- delay_codes %>% 
  mutate(description = coalesce(code_description_3, code_description_7),
         code = coalesce(sub_rmenu_code, srt_rmenu_code)
         ) %>% 
  select(code, description)
```

Coalesce didn't work because somtimes both sub_rmenu_code and srt_rmenu_code are available

```{r}
delay_codes <- delay_codes  %>%
  select(code = sub_rmenu_code, description = code_description_3) %>%
  remove_empty("rows") %>%
  bind_rows(
    delay_codes  %>%
              select(code = srt_rmenu_code, description = code_description_7) %>%
              remove_empty("rows")
  )
```




```{r}
delay_codes %>% count(code, sort = T)
```
















